Supplemental data to ``\emph{k}-mer-based GWAS enhances causal variant and candidate gene discovery in soybean''

### 2023-02-28 additional_files/additional_file_1.tex
Remove vg results from gene plots

% Figures mentioned in the main text
% Figures for flower color
\manhattanplot{flower_color}{flower color}{\getvar{flower_color_nsamples}}
\signalplot{flower_color_W1}{flower color}{\emph{W1}}%
{Vertical dotted lines indicate the location of the \getvar{flower_color_W1_gene} gene associated with the locus.}
\geneplot{flower_color_W1}{flower color}{\emph{W1}}{\getvar{flower_color_W1_gene} gene}%
{Vertical dotted lines in panels (c), (d) and (e) indicate the location of the causal SV at this locus.}
%\kmerplot{flower_color_W1}

% Figures for pubescence color
\manhattanplot{pubescence_color_all}{pubescence color (first GWAS)}{\getvar{pubescence_color_all_nsamples}}
\signalplot{pubescence_color_all_T}{pubescence color (first GWAS)}{\emph{T}}%
{Vertical dotted lines indicate the location of the \getvar{pubescence_color_all_T_gene} gene associated with the locus.}
\geneplot{pubescence_color_all_T}{pubescence color (first GWAS)}{\emph{T}}{\getvar{pubescence_color_all_T_gene} gene}%
{Vertical dotted lines in panels (b) and (e) indicate the location of the causal indel at this locus.}
\kmerplot{pubescence_color_all_T}{\getvar{pubescence_color_all_T_gene}}{\emph{T}}{pubescence color (first GWAS)}{a causal indel}

\manhattanplot{pubescence_color_nogray}{pubescence color (second GWAS)}{\getvar{pubescence_color_nogray_nsamples}}
\signalplot{pubescence_color_nogray_Td}{pubescence color (second GWAS)}{\emph{Td}}%
{Vertical dotted lines indicate the location of the \getvar{pubescence_color_nogray_Td_gene} gene associated with the locus.}
\geneplot{pubescence_color_nogray_Td}{pubescence color (second GWAS)}{\emph{Td}}{\getvar{pubescence_color_nogray_Td_gene} gene}%
{Vertical dotted lines in panels (b) and (e) indicate the location of the causal SNP at this locus.}
%\kmerplot{pubescence_color_nogray_Td}

@@

\manhattanplot{seed_coat_color_greenyellow}{seed coat color (second GWAS)}{\getvar{seed_coat_color_greenyellow_nsamples}}
\signalplot{seed_coat_color_greenyellow_G}{seed coat color (second GWAS)}{\emph{G}}%
{Vertical dotted lines indicate the location of the \getvar{seed_coat_color_greenyellow_G_gene} gene associated with the locus.}
\geneplot{seed_coat_color_greenyellow_G}{seed coat color (second GWAS)}{\emph{G}}{\getvar{seed_coat_color_greenyellow_G_gene} gene}%
{Vertical dotted lines in panels (b) and (e) indicate the location of the causal SNP at this locus.}
%\kmerplot{seed_coat_color_greenyellow_G}

% Figures for stem termination
\manhattanplot{stem_termination_all}{stem termination type (first GWAS)}{\getvar{stem_termination_all_nsamples}}
\signalplot{stem_termination_all_Dt1}{stem termination type (first GWAS)}{\emph{Dt1}}%
{Vertical dotted lines indicate the location of the \getvar{stem_termination_all_Dt1_gene} gene associated with the locus.}
\geneplot{stem_termination_all_Dt1}{stem termination type (first GWAS)}{\emph{Dt1}}{\getvar{stem_termination_all_Dt1_gene} gene}%
{Vertical dotted lines in panels (b) and (e) indicate the location of a causal SNP at this locus.}
\kmerplot{stem_termination_all_Dt1}{\getvar{stem_termination_all_Dt1_gene}}{\emph{Dt1}}{stem termination type (first GWAS)}{a causal SNP}

% Figures for hilum color
\manhattanplot{hilum_color_all}{hilum color (first GWAS)}{\getvar{hilum_color_all_nsamples}}
\signalplot{hilum_color_all_T}{hilum color (first GWAS)}{\emph{T}}%
{Vertical dotted lines indicate the location of the \getvar{hilum_color_all_T_gene} gene associated with the locus.}
\geneplot{hilum_color_all_T}{hilum color (first GWAS)}{\emph{T}}{\getvar{hilum_color_all_T_gene} gene}%
{Vertical dotted lines in panels (b) and (e) indicate the location of the causal indel at this locus.}
\kmerplot{hilum_color_all_T}{\getvar{hilum_color_all_T_gene}}{\emph{T}}{hilum color (first GWAS)}{a causal indel}
\signalplot{hilum_color_all_I}{hilum color (first GWAS)}{\emph{I}}%
{Vertical dotted lines indicate the boundaries of the tandem duplication/inversion identified as the causal variant at this locus.}

\manhattanplot{hilum_color_blackbrown}{hilum color (second GWAS)}{\getvar{hilum_color_blackbrown_nsamples}}
\signalplot{hilum_color_blackbrown_R}{hilum color (second GWAS)}{\emph{R}}%
{Vertical dotted lines indicate the location of the \getvar{hilum_color_blackbrown_R_gene} gene associated with the locus.}
\geneplot{hilum_color_blackbrown_R}{hilum color (second GWAS)}{\emph{R}}{\getvar{hilum_color_blackbrown_R_gene} gene}%
{Vertical dotted lines indicate the location an indel (panels b and e) and a SNP (panel e) that are putatively causal at this locus.}
\kmerplot{hilum_color_blackbrown_R}{\getvar{hilum_color_blackbrown_R_gene}}{\emph{R}}{hilum color (second GWAS)}{a SNP and an indel that are putatively causal}

@@

% Figures for pubescence form
\manhattanplot{pubescence_form_all}{pubescence form (first GWAS)}{\getvar{pubescence_form_all_nsamples}}
\signalplot{pubescence_form_all_Pa1}{pubescence form (first GWAS)}{\emph{Pa1}}%
{Vertical dotted lines indicate the location of the \getvar{pubescence_form_all_Pa1_gene} gene that we suggest as a candidate for this locus.}
\geneplot{pubescence_form_all_Pa1}{pubescence form (first GWAS)}{\emph{Pa1}}{\getvar{pubescence_form_all_Pa1_gene} candidate gene putatively}%
{Vertical dotted lines in panels (b) and (e) indicate the location of two highly significant non-synonymous SNPs at this gene.}
\kmerplot{pubescence_form_all_Pa1}{\getvar{pubescence_form_all_Pa1_gene} candidate}{\emph{Pa1}}{pubescence form (first GWAS)}{a non-synonymous SNP}
\signalplot{pubescence_form_all_Pa2}{pubescence form (first GWAS)}{\emph{Pa2}}{}

@@

% Pubescence density
\signalplot{pubescence_density_Ps}{pubescence density}{\emph{Ps}}%
{Vertical dotted lines indicate the boundaries of the causal CNV overlapping the \getvar{pubescence_density_Ps_gene} gene associated with the locus.}
\geneplot{pubescence_density_Ps}{pubescence density}{\emph{Ps}}{location of the causal CNV overlapping the \getvar{pubescence_density_Ps_gene} gene.}%
{The vertical dotted line in panel (e) indicates the location of the most significant \emph{k}-mer, which is associated with the causal CNV at this locus.
The shaded gray rectangles show the boundaries of the causal CNV.}

>>>>

% Figures mentioned in the main text
% Figures for flower color
\manhattanplot{flower_color}{flower color}{\getvar{flower_color_nsamples}}
\signalplot{flower_color_W1}{flower color}{\emph{W1}}%
{Vertical dotted lines indicate the location of the \getvar{flower_color_W1_gene} gene associated with the locus.}
\geneplot{flower_color_W1}{flower color}{\emph{W1}}{\getvar{flower_color_W1_gene} gene}%
{Vertical dotted lines in panels (c) and (d) indicate the location of the causal SV at this locus.}
%\kmerplot{flower_color_W1}

% Figures for pubescence color
\manhattanplot{pubescence_color_all}{pubescence color (first GWAS)}{\getvar{pubescence_color_all_nsamples}}
\signalplot{pubescence_color_all_T}{pubescence color (first GWAS)}{\emph{T}}%
{Vertical dotted lines indicate the location of the \getvar{pubescence_color_all_T_gene} gene associated with the locus.}
\geneplot{pubescence_color_all_T}{pubescence color (first GWAS)}{\emph{T}}{\getvar{pubescence_color_all_T_gene} gene}%
{Vertical dotted lines in panels (b) and (d) indicate the location of the causal indel at this locus.}
\kmerplot{pubescence_color_all_T}{\getvar{pubescence_color_all_T_gene}}{\emph{T}}{pubescence color (first GWAS)}{a causal indel}

\manhattanplot{pubescence_color_nogray}{pubescence color (second GWAS)}{\getvar{pubescence_color_nogray_nsamples}}
\signalplot{pubescence_color_nogray_Td}{pubescence color (second GWAS)}{\emph{Td}}%
{Vertical dotted lines indicate the location of the \getvar{pubescence_color_nogray_Td_gene} gene associated with the locus.}
\geneplot{pubescence_color_nogray_Td}{pubescence color (second GWAS)}{\emph{Td}}{\getvar{pubescence_color_nogray_Td_gene} gene}%
{Vertical dotted lines in panels (b) and (d) indicate the location of the causal SNP at this locus.}
%\kmerplot{pubescence_color_nogray_Td}

@@

\manhattanplot{seed_coat_color_greenyellow}{seed coat color (second GWAS)}{\getvar{seed_coat_color_greenyellow_nsamples}}
\signalplot{seed_coat_color_greenyellow_G}{seed coat color (second GWAS)}{\emph{G}}%
{Vertical dotted lines indicate the location of the \getvar{seed_coat_color_greenyellow_G_gene} gene associated with the locus.}
\geneplot{seed_coat_color_greenyellow_G}{seed coat color (second GWAS)}{\emph{G}}{\getvar{seed_coat_color_greenyellow_G_gene} gene}%
{Vertical dotted lines in panels (b) and (d) indicate the location of the causal SNP at this locus.}
%\kmerplot{seed_coat_color_greenyellow_G}

% Figures for stem termination
\manhattanplot{stem_termination_all}{stem termination type (first GWAS)}{\getvar{stem_termination_all_nsamples}}
\signalplot{stem_termination_all_Dt1}{stem termination type (first GWAS)}{\emph{Dt1}}%
{Vertical dotted lines indicate the location of the \getvar{stem_termination_all_Dt1_gene} gene associated with the locus.}
\geneplot{stem_termination_all_Dt1}{stem termination type (first GWAS)}{\emph{Dt1}}{\getvar{stem_termination_all_Dt1_gene} gene}%
{Vertical dotted lines in panels (b) and (d) indicate the location of a causal SNP at this locus.}
\kmerplot{stem_termination_all_Dt1}{\getvar{stem_termination_all_Dt1_gene}}{\emph{Dt1}}{stem termination type (first GWAS)}{a causal SNP}

% Figures for hilum color
\manhattanplot{hilum_color_all}{hilum color (first GWAS)}{\getvar{hilum_color_all_nsamples}}
\signalplot{hilum_color_all_T}{hilum color (first GWAS)}{\emph{T}}%
{Vertical dotted lines indicate the location of the \getvar{hilum_color_all_T_gene} gene associated with the locus.}
\geneplot{hilum_color_all_T}{hilum color (first GWAS)}{\emph{T}}{\getvar{hilum_color_all_T_gene} gene}%
{Vertical dotted lines in panels (b) and (d) indicate the location of the causal indel at this locus.}
\kmerplot{hilum_color_all_T}{\getvar{hilum_color_all_T_gene}}{\emph{T}}{hilum color (first GWAS)}{a causal indel}
\signalplot{hilum_color_all_I}{hilum color (first GWAS)}{\emph{I}}%
{Vertical dotted lines indicate the boundaries of the tandem duplication/inversion identified as the causal variant at this locus.}

\manhattanplot{hilum_color_blackbrown}{hilum color (second GWAS)}{\getvar{hilum_color_blackbrown_nsamples}}
\signalplot{hilum_color_blackbrown_R}{hilum color (second GWAS)}{\emph{R}}%
{Vertical dotted lines indicate the location of the \getvar{hilum_color_blackbrown_R_gene} gene associated with the locus.}
\geneplot{hilum_color_blackbrown_R}{hilum color (second GWAS)}{\emph{R}}{\getvar{hilum_color_blackbrown_R_gene} gene}%
{Vertical dotted lines indicate the location an indel (panels b and d) and a SNP (panel d) that are putatively causal at this locus.}
\kmerplot{hilum_color_blackbrown_R}{\getvar{hilum_color_blackbrown_R_gene}}{\emph{R}}{hilum color (second GWAS)}{a SNP and an indel that are putatively causal}

@@

% Figures for pubescence form
\manhattanplot{pubescence_form_all}{pubescence form (first GWAS)}{\getvar{pubescence_form_all_nsamples}}
\signalplot{pubescence_form_all_Pa1}{pubescence form (first GWAS)}{\emph{Pa1}}%
{Vertical dotted lines indicate the location of the \getvar{pubescence_form_all_Pa1_gene} gene that we suggest as a candidate for this locus.}
\geneplot{pubescence_form_all_Pa1}{pubescence form (first GWAS)}{\emph{Pa1}}{\getvar{pubescence_form_all_Pa1_gene} candidate gene putatively}%
{Vertical dotted lines in panels (b) and (d) indicate the location of two highly significant non-synonymous SNPs at this gene.}
\kmerplot{pubescence_form_all_Pa1}{\getvar{pubescence_form_all_Pa1_gene} candidate}{\emph{Pa1}}{pubescence form (first GWAS)}{a non-synonymous SNP}
\signalplot{pubescence_form_all_Pa2}{pubescence form (first GWAS)}{\emph{Pa2}}{}

@@

% Pubescence density
\signalplot{pubescence_density_Ps}{pubescence density}{\emph{Ps}}%
{Vertical dotted lines indicate the boundaries of the causal CNV overlapping the \getvar{pubescence_density_Ps_gene} gene associated with the locus.}
\geneplot{pubescence_density_Ps}{pubescence density}{\emph{Ps}}{location of the causal CNV overlapping the \getvar{pubescence_density_Ps_gene} gene.}%
{The vertical dotted line in panel (d) indicates the location of the most significant \emph{k}-mer, which is associated with the causal CNV at this locus.
The shaded gray rectangles show the boundaries of the causal CNV.}

### 2023-02-28 additional_files/manuscript.tex
Remove vg results from gene plots

% Defining a new command for gene plot figures
\newcommand{\geneplot}[5]{
\begin{cfigure}
	\includegraphics[width = 5.8in]{#1_gene}
	\caption[Zoomed-in Manhattan plots of the #3 locus gene]%
	{Zoomed-in Manhattan plots generated from the GWAS analysis of #2 at the #4 associated with the #3 locus using four genotype datasets:
	(b) Platypus (SNPs and indels), (c) vg (SVs), (d) Paragraph (SVs), (e) \emph{k}-mers presence/absence.
	#5
	Horizontal dotted lines indicate the 5\% family-wise error-rate significance threshold determined from a randomization approach.
	In the case of Platypus, blue points denote markers used in the original analysis, whereas red points denote points that had originally been pruned but whose
	\emph{p}-values were computed after signal discovery.
	Panel (a) shows gene models over the plotting interval.
	Exons are represented by rectangles whereas introns are represented by horizontal lines.
	Coding sequences are shown in blue and the direction of transcription is indicated by arrows.
	}
	\label{#1_gene}
\end{cfigure}

>>>>

% Defining a new command for gene plot figures
\newcommand{\geneplot}[5]{
\begin{cfigure}
	\includegraphics[width = 5.8in]{#1_gene}
	\caption[Zoomed-in Manhattan plots of the #3 locus gene]%
	{Zoomed-in Manhattan plots generated from the GWAS analysis of #2 at the #4 associated with the #3 locus using three genotype datasets:
	(b) Platypus (SNPs and indels), (c) Paragraph (SVs), (d) \emph{k}-mers presence/absence.
	#5
	Horizontal dotted lines indicate the 5\% family-wise error-rate significance threshold determined from a randomization approach.
	In the case of Platypus, blue points denote markers used in the original analysis, whereas red points denote points that had originally been pruned but whose
	\emph{p}-values were computed after signal discovery.
	Panel (a) shows gene models over the plotting interval.
	Exons are represented by rectangles whereas introns are represented by horizontal lines.
	Coding sequences are shown in blue and the direction of transcription is indicated by arrows.
	}
	\label{#1_gene}
\end{cfigure}
